---
title: "Extra code"
author: "Kathryn Denning"
date: "1/12/2021"
output: html_document
---

## Adding in PT unspecified

```{r meta overall ptus data prep}
meta_overall_ptus <- meta_data %>% 
  mutate(pt_comparison = fct_collapse(pt_comparison, 
                                      pt_v_control = c("1", "2", "5", "6", "10", "11"),
                                      pt_v_objective = c("3", "7", "12"))) %>% 
  filter(pt_comparison == "pt_v_control" | pt_comparison == "pt_v_objective") %>% 
  mutate(pt_comparison = as.factor(droplevels(pt_comparison)),
         dunb = ifelse(outcome_type == "1",
                       dunb*-1,
                       ifelse(outcome_type != "1",
                              dunb*1, NA)),
         outcome_type = recode(outcome_type,
                               `3` = "Interpersonal Feels",
                               `2` = "Overlap",
                               `1` = "Stereotyping")) 

```

### Overall meta-analytic effect before we look into theoretical moderators with PTUS

```{r meta overall ptus no mods}
meta_overall_ptus_model <- rma.mv(dunb, 
                      var_dunb,
                      random = list(~ 1 | sample_number_total/conditions_within_sample_var/outcomes_within_sample_var, 
                                    ~ 1 | outcome_scale_group), data = meta_overall_ptus)
meta_overall_ptus_model
```

Slightly larger, but not much different than without adding PT unspecified.

### Multivariate model with perspective taking only with PTUS

```{r meta overall ptus pt mod}
#setting up dummy codes; stereotyping and pt_v_control are the respective comparison groups because they are coded as 1
contrasts(meta_overall_ptus$pt_comparison) <- contr.treatment(2)
contrasts(meta_overall_ptus$pt_comparison) 

# OVerall model across outcome type
meta_multi1_ptus <- rma.mv(dunb, 
                      var_dunb, 
                      mods = ~ pt_comparison,
                      random = list(~ 1 | sample_number_total/conditions_within_sample_var/outcomes_within_sample_var, 
                                    ~ 1 | outcome_scale_group), data = meta_overall_ptus)

meta_multi1_ptus
```

Pattern did not change - slight increase in intercept estimate (representing pt_v_control) and slight decrease in pt_v_objective estimate, but significance did not change.

## Pre-registered multivariate model with perspective taking and outcome type with PTUS

```{r meta overall interaction ptus}
contrasts(meta_overall_ptus$outcome_type) <- contr.treatment(3)
contrasts(meta_overall_ptus$outcome_type) 

# When we include outcome type
meta_multi2_ptus <- rma.mv(dunb, 
                      var_dunb, 
                      mods = ~ pt_comparison*outcome_type,
                      random = list(~ 1 | sample_number_total/conditions_within_sample_var/outcomes_within_sample_var, 
                                    ~ 1 | outcome_scale_group), data = meta_overall_ptus)
meta_multi2_ptus
```

On the interaction (the part that really matters to us), the pattern of results did not change.

All possible pairwise comparisons with PTUS included:

```{r pairwise comparisons ptus}
summary(glht(meta_multi2_ptus, linfct=contrMat(c("pt_v_control:Stereotyping"=1,
                                            "pt_v_control:Overlap"=1,
                                            "pt_v_control:Interpersonal Feels"=1,
                                       "pt_v_objective:Stereotyping"=1,
                                       "pt_v_objective:Overlap"=1,
                                       "pt_v_objective:Interpersonal Feels"=1), 
                                       type="Tukey")), 
        test=adjusted("none"))

```

When adding in PTUS, a few more pairwise comparisons become significant or trending.The comparison that is newly significant that was previously NS: pt_v_objective:Interpersonal Feels - pt_v_objective:Stereotyping == 0. The comparison that was previously NS that is now trending: pt_v_objective:Overlap - pt_v_control:Overlap == 0 (but .099 trending...).  

### Output from individual models to obtain effect sizes per instruction and comparison set:

```{r overall meta pt v control stereo ptus}
meta_overall_subset_ptus <- meta_overall_ptus %>% 
  filter(pt_comparison == "pt_v_control" & outcome_type == "Stereotyping")


meta_control_stereo_ptus <- rma.mv(dunb, 
                      var_dunb, 
                      random = list(~ 1 | sample_number_total/conditions_within_sample_var/outcomes_within_sample_var, 
                                    ~ 1 | outcome_scale_group), data = meta_overall_subset_ptus)
```

```{r overall meta pt v control overlap ptus}
control_overlap_subset_ptus <- meta_overall_ptus %>% 
  filter(pt_comparison == "pt_v_control" & outcome_type == "Overlap")


meta_control_overlap_ptus <- rma.mv(dunb, 
                      var_dunb, 
                      random = list(~ 1 | sample_number_total/conditions_within_sample_var/outcomes_within_sample_var, 
                                    ~ 1 | outcome_scale_group), data = control_overlap_subset_ptus)
```

```{r overall meta pt v control interpersonal ptus}
control_inter_subset_ptus <- meta_overall_ptus %>% 
  filter(pt_comparison == "pt_v_control" & outcome_type == "Interpersonal Feels")
```

Pairwise comparisons:

* pt_comparison2:outcome_type2:target_information2 - pt_comparison2:outcome_type3:target_information2

```{r pairwise comparisons overall meta target info mod 1}
anova(meta_multi4, btt=15:16)
```

NS - The difference between these two comparisons is outcome category (merging vs stereotyping), with pt_v_control and medium target information help constant.

* pt_comparison2:outcome_type2:target_information2 - pt_comparison2:outcome_type2:target_information3 

```{r pairwise comparisons overall meta target info mod 2}
anova(meta_multi4, btt=15:17)
```

Sig - The difference between these two is target information, they are both the merging outcome category, but one is medium target information and one is detailed.

* pt_comparison2:outcome_type2:target_information2 - pt_comparison2:outcome_type3:target_information3

```{r pairwise comparisons overall meta target info mod 3}
anova(meta_multi4, btt=15:18)
```

Sig - There is a significant difference between merging/medium target information and stereotyping/detailed target information.

* pt_comparison2:outcome_type3:target_information2 - pt_comparison2:outcome_type2:target_information3 

```{r pairwise comparisons overall meta target info mod 4}
anova(meta_multi4, btt=16:17)
```

NS - These is not a difference when stereotyping has medium target information and it is compared to merging with detailed information and pt_v_control is help constant. This is weird, since the contrast with opposing groupings (stereotyping/high detail vs merging/medium detail).

* pt_comparison2:outcome_type3:target_information2 - pt_comparison2:outcome_type3:target_information3 

```{r pairwise comparisons overall meta target info mod 5}
anova(meta_multi4, btt=16:18)
```

NS

* pt_comparison2:outcome_type2:target_information3 - pt_comparison2:outcome_type3:target_information3 

```{r pairwise comparisons overall meta target info mod 5}
anova(meta_multi4, btt=17:18)
```

Marginal - When pt_v_control and detailed target information is held constant, there is a difference between merging and stereotyping outcome groups.


meta_control_inter_ptus <- rma.mv(dunb, 
                      var_dunb, 
                      random = list(~ 1 | sample_number_total/conditions_within_sample_var/outcomes_within_sample_var, 
                                    ~ 1 | outcome_scale_group), data = control_inter_subset_ptus)
```

```{r overall meta pt vs objective stereo ptus}
obj_stereo_subset_ptus <- meta_overall_ptus %>% 
  filter(pt_comparison == "pt_v_objective" & outcome_type == "Stereotyping")


meta_obj_stereo_ptus <- rma.mv(dunb, 
                      var_dunb, 
                      random = list(~ 1 | sample_number_total/conditions_within_sample_var/outcomes_within_sample_var, 
                                    ~ 1 | outcome_scale_group), data = obj_stereo_subset_ptus)
```

```{r overall meta pt vs objective overlap ptus}
obj_overlap_subset_ptus <- meta_overall_ptus %>% 
  filter(pt_comparison == "pt_v_objective" & outcome_type == "Overlap")


meta_obj_overlap_ptus <- rma.mv(dunb, 
                      var_dunb, 
                      random = list(~ 1 | sample_number_total/conditions_within_sample_var/outcomes_within_sample_var, 
                                    ~ 1 | outcome_scale_group), data = obj_overlap_subset_ptus)
```

```{r overall meta pt vs objective interpersonal ptus}
obj_inter_subset_ptus <- meta_overall_ptus %>% 
  filter(pt_comparison == "pt_v_objective" & outcome_type == "Interpersonal Feels")


meta_obj_inter_ptus <- rma.mv(dunb, 
                      var_dunb, 
                      random = list(~ 1 | sample_number_total/conditions_within_sample_var/outcomes_within_sample_var, 
                                    ~ 1 | outcome_scale_group), data = obj_inter_subset_ptus)
```

```{r overall meta effect table ptus}
effect_table_ptus <- cbind(label = c("Pt vs Control in Stereotyping", 
                              "PT vs Objective in Stereotyping",
                              "PT vs Control in Overlap",
                              "PT vs Cobjective in Overlap",
                              "PT vs Control in Interpersonal feelings",
                              "PT vs Objective in Interpersonal feelings"),
                      estimate = c(meta_control_stereo_ptus[1],
                                 meta_obj_stereo_ptus[1],
                                 meta_control_overlap_ptus[1],
                                 meta_obj_overlap_ptus[1],
                                 meta_control_inter_ptus[1],
                                 meta_obj_inter_ptus[1]),
                      pvalue = c(meta_control_stereo_ptus[5],
                                 meta_obj_stereo_ptus[5],
                                 meta_control_overlap_ptus[5],
                                 meta_obj_overlap_ptus[5],
                                 meta_control_inter_ptus[5],
                                 meta_obj_inter_ptus[5]),
                      ci_upper = c(meta_control_stereo_ptus[6],
                                 meta_obj_stereo_ptus[6],
                                 meta_control_overlap_ptus[6],
                                 meta_obj_overlap_ptus[6],
                                 meta_control_inter_ptus[6],
                                 meta_obj_inter_ptus[6]),
                      ci_lower = c(meta_control_stereo_ptus[7],
                                 meta_obj_stereo_ptus[7],
                                 meta_control_overlap_ptus[7],
                                 meta_obj_overlap_ptus[7],
                                 meta_control_inter_ptus[7],
                                 meta_obj_inter_ptus[7]))
effect_table_ptus 
```

In comparing the two tables, the only significant difference in effect sizes is that the estimate in "PT vs control" condition in the stereotyping outcome increases from .039 to .101. However, it is still not significantly different from 0. The other estimates are all approximately the same.

# Code from when I wrote every all multi models by hand

```{r overall model pt vs control stereo}
control_stereo_subset <- meta_overall1 %>% 
  filter(pt_comparison == "pt_v_control" & outcome_type == "Stereotyping")

meta_control_stereo <- rma.mv(dunb, 
                      var_dunb, 
                      random = list(~ 1 | sample_number_total/outcomes_within_sample_var, 
                                    ~ 1 | outcome_scale_group), data = control_stereo_subset )

stereo_control_I2 <- get_I2_overall(control_stereo_subset, meta_control_stereo)
get_I2_var_levels(control_stereo_subset, meta_control_stereo)
```

```{r overall model pt v control overlap}
control_overlap_subset <- meta_overall1 %>% 
  filter(pt_comparison == "pt_v_control" & outcome_type == "Overlap")

meta_control_overlap <- rma.mv(dunb, 
                      var_dunb, 
                      random = list(~ 1 | sample_number_total/outcomes_within_sample_var, 
                                    ~ 1 | outcome_scale_group), data = control_overlap_subset)

overlap_control_I2 <- get_I2_overall(control_overlap_subset, meta_control_overlap)
```

```{r overall model pt v control interpersonal}
control_inter_subset <- meta_overall1 %>% 
  filter(pt_comparison == "pt_v_control" & outcome_type == "Interpersonal Feels")

meta_control_inter <- rma.mv(dunb, 
                      var_dunb, 
                      random = list(~ 1 | sample_number_total/outcomes_within_sample_var, 
                                    ~ 1 | outcome_scale_group), data = control_inter_subset)

inter_control_I2 <- get_I2_overall(control_inter_subset, meta_control_inter)
```

```{r overall model pt v objective stereo}
obj_stereo_subset <- meta_overall1 %>% 
  filter(pt_comparison == "pt_v_objective" & outcome_type == "Stereotyping")

meta_obj_stereo <- rma.mv(dunb, 
                      var_dunb, 
                      random = list(~ 1 | sample_number_total/outcomes_within_sample_var, 
                                    ~ 1 | outcome_scale_group), data = obj_stereo_subset)

stereo_object_I2 <- get_I2_overall(obj_stereo_subset, meta_obj_stereo)
```

```{r overall model pt v objective overlap}
obj_overlap_subset <- meta_overall1 %>% 
  filter(pt_comparison == "pt_v_objective" & outcome_type == "Overlap")

meta_obj_overlap <- rma.mv(dunb, 
                      var_dunb, 
                      random = list(~ 1 | sample_number_total/outcomes_within_sample_var, 
                                    ~ 1 | outcome_scale_group), data = obj_overlap_subset)

overlap_object_I2 <- get_I2_overall(obj_overlap_subset, meta_obj_overlap)
```

```{r overall model pt v objective interpersonal }
obj_inter_subset <- meta_overall1 %>% 
  filter(pt_comparison == "pt_v_objective" & outcome_type == "Interpersonal Feels")

meta_obj_inter <- rma.mv(dunb, 
                      var_dunb, 
                      random = list(~ 1 | sample_number_total/outcomes_within_sample_var, 
                                    ~ 1 | outcome_scale_group), data = obj_inter_subset)

inter_object_I2 <- get_I2_overall(obj_inter_subset, meta_obj_inter)
```

```{r overall model effect size table}
effect_table <- cbind(label = c("Pt vs Control in Stereotyping", 
                              "PT vs Objective in Stereotyping",
                              "PT vs Control in Overlap",
                              "PT vs Cobjective in Overlap",
                              "PT vs Control in Interpersonal feelings",
                              "PT vs Objective in Interpersonal feelings"),
                      estimate = c(meta_control_stereo[1],
                                 meta_obj_stereo[1],
                                 meta_control_overlap[1],
                                 meta_obj_overlap[1],
                                 meta_control_inter[1],
                                 meta_obj_inter[1]),
                      pvalue = c(meta_control_stereo[5],
                                 meta_obj_stereo[5],
                                 meta_control_overlap[5],
                                 meta_obj_overlap[5],
                                 meta_control_inter[5],
                                 meta_obj_inter[5]),
                      ci_upper = c(meta_control_stereo[6],
                                 meta_obj_stereo[6],
                                 meta_control_overlap[6],
                                 meta_obj_overlap[6],
                                 meta_control_inter[6],
                                 meta_obj_inter[6]),
                      ci_lower = c(meta_control_stereo[7],
                                 meta_obj_stereo[7],
                                 meta_control_overlap[7],
                                 meta_obj_overlap[7],
                                 meta_control_inter[7],
                                 meta_obj_inter[7]),
                      I2 = c(stereo_control_I2[1],
                             stereo_object_I2[1],
                             overlap_control_I2[1],
                             overlap_object_I2[1],
                             inter_control_I2[1],
                             inter_object_I2[1]))

effect_table
```
