---
title: 'Perspective Taking Meta-Analysis: Prelims Version'
author: "Kathryn Denning"
date: "1/9/2021"
output: html_document
---


```{r setup data import and cleaning, echo = FALSE, warning = FALSE, message = FALSE, error = FALSE}
# Cleaning
## import data

#install.packages("rio")
#install.packages("here")
#install.packages("tidyverse")
#install.packages("magrittr")
#install.packages("janitor")
#install.packages("lme4")
#install.packages("emmeans")
#install.packages("metafor")
#install.packages("Cairo")
#install.packages("tinytex")
#install.packages("compute.es")
library(rio)
library(here)
library(tidyverse)
library(magrittr)
library(janitor)
library(lme4)
library(emmeans)
library(Cairo)
library(tinytex)
library(metafor)
library(compute.es)

# Setting global chunk options
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

# Windows messes up my plots, these lines of code make them clearer
knitr::opts_knit$set(dev.args = list(type = "cairo"))

trace(grDevices:::png, quote({
  if (missing(type) && missing(antialias)) {
    type <- "cairo-png"
    antialias <- "subpixel"
  }
}), print = FALSE)

# importing data
prelims_data <- import("prelims_data.xlsx") 
```

# Convert effect sizes and CI around it

## Convert F to d

```{r}
f_to_d <- prelims_data %>% 
  select(effect_size_num, F_score, n_pt, n_comparison) %>% 
  filter(F_score != "NA")

f_to_d_output <- fes(f = F_score, n.1 = n_pt, n.2 = n_comparison, level = 95, id = effect_size_num, data = f_to_d) #function drops 95CI when producing table for some reason

f_to_d_output %<>% 
  select(id, d, var.d) %>% 
  mutate(effect_size_num = id,
         var_d = var.d) %>% 
  select(-var.d,-id)

prelims_data_fconverted <- left_join(prelims_data, f_to_d_output, by = "effect_size_num")
```

## Convert t to d

```{r}

t_to_d <- prelims_data_fconverted %>% 
  select(effect_size_num, t_score, n_pt, n_comparison) %>% 
  filter(t_score!= "NA")

t_to_d_output <- tes(t = t_score, n.1 = n_pt, n.2 = n_comparison, level = 95, id = effect_size_num, data = t_to_d)

t_to_d_output %<>% 
  select(id, d, var.d) %>% 
  mutate(effect_size_num = id,
         var_d = var.d) %>% 
  select(-var.d,-id)


prelims_data_ftconverted <- left_join(prelims_data_fconverted, t_to_d_output, by = "effect_size_num")
```

## Convert means/sds to d

```{r}
# Getting dataset of values that do not have 
mean_sd_data <- prelims_data_ftconverted %>% 
  select(effect_size_num, mean_pt, mean_comparison, sd_pt, 
         sd_comparison, n_pt, n_comparison, cohens_d, d.x, d.y) %>% 
  filter(!is.na(mean_pt) & !is.na(mean_comparison) & !is.na(sd_pt) 
         & !is.na(sd_comparison) & is.na(cohens_d))

msd_to_d <- escalc(measure = "SMD", m1i = mean_pt, m2i = mean_comparison, sd1i = sd_pt, sd2i = sd_comparison, n1i = n_pt, n2i = n_comparison, data = mean_sd_data, vtype = "UB") #since we will have to unbias other cohen's d, told escalc to calculate an unbiased SMD

#yi in the output is SMD, vi is sampling variance

msd_to_d %<>% 
  select(effect_size_num, yi, vi)

converted_data <- left_join(prelims_data_ftconverted, msd_to_d, by = "effect_size_num")

```

## Convert regression coefficients to d

We need SD of the DV - which most studies did not provide - in order to convert this. We will need to add these studies (k = 21) to our "Contact Authors" sheet if they are not already on there for some reason.

# Other data prep

```{r}

meta_data <- converted_data %>%  
  mutate(cohens_d = as.numeric(cohens_d)) %>% 
  mutate(cohens_d_var = (((n_pt + n_comparison)/(n_pt*n_comparison)) + ((cohens_d^2)/(2*(n_pt+n_comparison))))) %>% #calculated variance by hand for the d's we extracted from articles directly; the ones we converted also came with var calculations
  pivot_longer(c(cohens_d, d.x, d.y, yi)) %>% #  Wrangling all converted d's into one column
  mutate(d = value) %>% 
  filter(!is.na(d)) %>% 
  select(-c(name, value)) %>% 
  pivot_longer(c(cohens_d_var, var_d.x, var_d.y, vi)) %>% #wrangling all variances into one column
  mutate(var = value) %>% 
  filter(!is.na(var)) %>% 
  select(-c(name, value)) %>% 
  mutate(df = (n_pt + n_comparison - 2), #getting degrees of freedom
         J = 1- (3/((4*df)-1)), #calculating hedges correction factor for d unbiased
         dunb = J*d, #d unbiased
         var_dunb = ((J^2)*var),  #variance for d unbiased
         lowCI_dunb = dunb-1.96*sqrt(var_dunb), #getting 95% CI's for d unbiased
         upCI_dunb  = dunb+1.96*sqrt(var_dunb)) 

```

## Convert all d's to d unbiased

# reverse score relevant d's
